---
title: "Exercise 3.30"
author: Xiaozhu Zhang
output: html_notebook
---
```{r, message=FALSE}
library(nimble)
library(TeachingDemos)
library(ggplot2)
```

# 1. HPD for $\sigma^2$ 
The posterior for $\sigma^2$ is
\[ \pi(\sigma^2|t) = \sigma^{-4} e^{-1/\sigma^2},  \]
which is exactly the Inverse-Gamma distribution $\Gamma^{-1}(1,1)$. Therefore, the 95% HPD can be obtained by
```{r}
hpd(qinvgamma, shape = 1)
```

# 2. HPD for $\sigma$
However, the posterior for $\sigma$ is
\[\pi(\sigma|t) = 2 \sigma^{-3} e^{-1/\sigma^2},  \]
which is a rather uncommon distribution. In order to find the HPD, we first need to sample enough values from this distribution, using the accept-reject method.

**Step 1: the proposal distribution.**

We can use the Inverse-Gamma distribution $\Gamma^{-1}(1,1)$ as the proposal distribution. Set $c = 2.1$. Such a choice is justified by the following test and graph. 
```{r, fig.height= 4, fig.width=8, fig.align='center'}
set.seed(54321)
# The target distribution
f <- function(x){
  2 * x^(-3) * exp(-1/x^2)
}

# Test the validity of proposal distribution
seq <- sapply(seq(0.01, 20, 0.01), f)
gam <- sapply(seq(0.01, 20, 0.01), function(x){
  dinvgamma(x, shape = 1)})
gam.n <- gam * 2.1

# Number of invalid points
sum(gam.n <= seq)

# Visualization
gp <- c(rep(0,length(seq)), rep(1, length(gam.n)))
df <- data.frame(x = c(seq(0.01, 20, 0.01), seq(0.01, 20, 0.01)),
                 y = c(seq, gam.n),
                 gp = as.factor(gp))

ggplot(data = df, aes(x = x, y = y, color = gp)) +
  geom_point() +
  scale_color_discrete(name = "Density", labels = c("Target", "Proposal")) +
  ylab("Density")
```

In a nutshell, there is no invalid points, and the graph above shows that the proposal distribution is completely above the target distribution.

**Step 2: the accept-reject procedure.**

```{r}
c = 2.1
n = 1e6
# Sample from the proposal distribution
x.star <- rinvgamma(n, shape = 1)

# Compute the acceot-reject threshold
ratio <- sapply(x.star, f) / (c * sapply(x.star, function(x){dinvgamma(x, shape = 1)})) 

# Decide to accept or not
u <- runif(n)
ind <- u <= ratio

# Obtain the sample values
x.final <- x.star[ind]
length(x.final)
```

With the sampled values `x.final`, we can finaly find the 95% HPD of $\sigma$:
```{r}
emp.hpd(x.final)
```

# 3. Conclusion
Since $\sigma^2$ and $\sigma$ are from different distributions, we can presume that they have different HPD even without computing. Now that the HPD for $\sigma^2$ is about [0.093, 19.504], while the HPD for $\sigma$ is about [0.365, 4.444], the presumption is indeed true. However, if we square the HPD for $\sigma$:
```{r}
emp.hpd(x.final)^2
```
we can say that it is quite close to the interval for $\sigma^2$, though not exactly the same.


